%-------------------------
% Resume in Latex
% Author : Vansh Gambhir
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeCompanyHeading}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeRoleHeading}[2]{
  \vspace{3pt}
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Vansh Gambhir} & Email : {vansh.gambhir@gmail.com}\\
  {www.vansh.dev} & Mobile : {+1 (425) 595-8895} \\
  {linkedin.com/in/vanshgambhir}\\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Washington}{Seattle, WA}{Dean's List (multiple years)}{September 2015 -- June 2020}
  \resumeSubHeadingListEnd

%-----------SKILLS---------------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Web Development: }
      {CSS, HTML, ReactJS, Vue, NodeJS, ExpressJS, Laravel, HapiJS, Vite, Docker, GitHub Actions, Vercel}{}
    \resumeSubItem{Languages: }
      {TypeScript, JavaScript, PHP, Python, Java, Go, Swift}{}
    \resumeSubItem{Testing: }
      {Cypress, Playwright, Vitest, React Testing Library}{}
    \resumeSubItem{AWS Tools: }
      {CloudFront, EC2, S3, SNS, IAM, Lambda, CloudWatch, AppSync, ChatBot, Bedrock, IoT Core}{}
    \resumeSubItem{Data: }
      {Cassandra, MySQL, DynamoDB, MongoDB}{}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {BRINC Drones}{Seattle, WA}
      {Software Engineer}{Feb 2026 -- Present}
      \resumeItemListStart
        \resumeItem{}{Building the LiveOps platform, focused on the piloting and flight control experience for drone operators.}
        \resumeItem{}{Developing features that directly interface with drone hardware, maintaining a highly performant UI under real-time constraints using Vue, TypeScript, PHP, Laravel, and EC2.}
      \resumeItemListEnd

    \resumeCompanyHeading
      {Amazon Web Services}{Seattle, WA}

      \resumeRoleHeading{Front End Engineer 2 (GenAI Agents)}{Jan 2025 -- Feb 2026}
      \resumeItemListStart
        \resumeItem{}{Led a team of 3 to architect and build the rendering engine for AWS Q Automate from scratch using React, TypeScript, and a custom layout algorithm; renders complex automation DSLs into deterministic, interactive node graphs capable of handling 1,000+ nodes with smooth performance, comparable in experience to n8n. Onboarded the entire frontend org to the new architecture.}
        \resumeItem{}{Co-developed a DSL with Applied Scientists that interfaces directly with a trained model, supporting 50+ coding constructs and 300+ connectors. Served as security guardian for the frontend team, reviewing all new features and architectural decisions, and partnered with AppSec engineers to keep threat models current.}
      \resumeItemListEnd

      \resumeRoleHeading{Front End Engineer II (App Studio \& QApps)}{July 2020 -- Jan 2025}
      \resumeItemListStart
        \resumeItem{}{Under tight constraints, delivered AWS AppStudio as a 0-1 product: architected a spec-driven rendering system that compiles customer-defined schemas into React components at runtime, forming the foundation of a no-code app builder. Led a team of 5 from architecture through GA.}
        \resumeItem{}{Built abstractions over Redshift, QuickSight, S3, Lambda, and Bedrock, enabling customers to integrate AWS services without deep infrastructure knowledge.}
        \resumeItem{}{Built in-house devtools enabling 35\% faster feature delivery. Revamped metrics and alarms across 3 teams; created org-wide E2E infrastructure with Cypress.}
      \resumeItemListEnd

    \resumeSubheading
      {Apple, Inc}{Cupertino, CA}
      {Software Engineer Intern}{June 2019 -- September 2019}
      \resumeItemListStart
        \resumeItem{}{Built a RESTful API and React/Node UI from scratch to configure LDAP-based feature flags, enabling safe staged rollouts for internal developers. Designed the Cassandra schema for the service.}
        \resumeItem{}{Contributed to the launch of Apple's internal design system, documenting and fixing components via StorybookJS.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Selected Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {vansh.dev}{}
      {React, TypeScript, Vite, Claude API, Vercel, GitHub Actions}{}
      \resumeItemListStart
        \resumeItem{}{Built a VS Code-themed interactive portfolio featuring an AI chat assistant powered by Claude, a command palette, syntax-highlighted code panels, a mock terminal with Easter eggs, and full keyboard and screen reader accessibility.}
        \resumeItem{}{Hardened the Claude agent with prompt injection defenses, input sanitization, and structured system prompts; wrote agent behavior tests to validate response quality. Set up CI/CD via GitHub Actions and Vercel, and integrated API-level logging for observability.}
      \resumeItemListEnd

    \resumeSubheading
      {SkiBud}{Seattle, WA}
      {MS SQL Management Studio, Python}{}
      \resumeItemListStart
        \resumeItem{}{Designed a ski resort management database on MS SQL Server. Populated via BeautifulSoup, built stored procedures and synthetic transactions validating 100,000+ INSERT throughput, and authored an SLA with disaster-recovery plans.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
